\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-22 paper.qmd
Added equations

sc_ltr_pos <- c(0.08, 0.96)
# sc_xlims <- c(-0.25, 1.25)
# sc_ylims <- c(-0.25, 2.59)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.25, 1.8)

@@

The 2D hexagon grid is defined by the number of bins in each direction ($b_1, b_2$), and the lower left position where the grid starts ($s_1, s_2$). The values of $s_i$ need to be below their respective minimum variable values, and could be a full bin lower, to allow a buffer corresponding to a full hexagon width and height around the data. The values of $b_i$ are variables to be computed that define the reduction in size of the data ($n$ to $m$).

@@

@@

@@

Define a hexagonal grid across the \kD{} space, using hexagons with fixed height ($a_1$), width ($a_2$). Each of the \kD{} points will belong to a hexagonal bin. That is, for each $y \in \mathbfit{Y}$, we can (uniquely) identify the hexagon that the point belongs to. This identification is done finding the nearest bin centroid for the \kD{} points by considering the \kD{} Euclidean distance.

When $k=2$, the starting coordinates $(s_1, s_2)$ mark the lower left of the grid. This is the bottom left bin centroid. By starting from there, points are generated to fill the grid accounting $b_1$, $b_2$, $a_2$, and $a_1$.

>>>>

sc_ltr_pos <- c(0.08, 0.96)
# sc_xlims <- c(-0.25, 1.25)
# sc_ylims <- c(-0.25, 2.59)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.25, 2)

@@

The 2D hexagon grid is defined by the number of bins in each direction ($b_1, b_2$), and the lower left position where the grid starts ($s_1, s_2$). The values of $s_i$ need to be below their respective minimum variable values, and could be a full bin lower, to allow a buffer corresponding to a full hexagon width ($a_1$) and height ($a_2$) around the data. The values of $b_i$ are variables to be computed that define the reduction in size of the data ($n$ to $m$).

@@

$$
b_1 = \frac{r_1 + q_1}{a_1}.
$$

@@

$$
b_2 = \frac{r_2 + q_2}{0.75 \times a_2}.
$$

@@

Define a hexagonal grid across the \kD{} space, using hexagons with fixed height ($a_2$), width ($a_1$). Each of the \kD{} points will belong to a hexagonal bin. That is, for each $y \in \mathbfit{Y}$, we can (uniquely) identify the hexagon that the point belongs to. This identification is done finding the nearest bin centroid for the \kD{} points by considering the \kD{} Euclidean distance.

When $k=2$, the starting coordinates $(s_1, s_2)$ mark the lower left of the grid. This is the bottom left bin centroid. By starting from there, points are generated to fill the grid accounting $b_1$, $b_2$, $a_1$, and $a_2$.

### 2024-04-22 paper.tex
Added equations

The 2D hexagon grid is defined by the number of bins in each direction
(\(b_1, b_2\)), and the lower left position where the grid starts
(\(s_1, s_2\)). The values of \(s_i\) need to be below their respective
minimum variable values, and could be a full bin lower, to allow a
buffer corresponding to a full hexagon width and height around the data.
The values of \(b_i\) are variables to be computed that define the
reduction in size of the data (\(n\) to \(m\)).

@@

@@

@@

Define a hexagonal grid across the \kD{} space, using hexagons with
fixed height (\(a_1\)), width (\(a_2\)). Each of the \kD{} points will
belong to a hexagonal bin. That is, for each \(y \in \mathbfit{Y}\), we
can (uniquely) identify the hexagon that the point belongs to. This
identification is done finding the nearest bin centroid for the \kD{}
points by considering the \kD{} Euclidean distance.

When \(k=2\), the starting coordinates \((s_1, s_2)\) mark the lower
left of the grid. This is the bottom left bin centroid. By starting from
there, points are generated to fill the grid accounting \(b_1\),
\(b_2\), \(a_2\), and \(a_1\).

>>>>

The 2D hexagon grid is defined by the number of bins in each direction
(\(b_1, b_2\)), and the lower left position where the grid starts
(\(s_1, s_2\)). The values of \(s_i\) need to be below their respective
minimum variable values, and could be a full bin lower, to allow a
buffer corresponding to a full hexagon width (\(a_1\)) and height
(\(a_2\)) around the data. The values of \(b_i\) are variables to be
computed that define the reduction in size of the data (\(n\) to \(m\)).

@@

\[
b_1 = \frac{r_1 + q_1}{a_1}.
\]

@@

\[
b_2 = \frac{r_2 + q_2}{0.75 \times a_2}.
\]

@@

Define a hexagonal grid across the \kD{} space, using hexagons with
fixed height (\(a_2\)), width (\(a_1\)). Each of the \kD{} points will
belong to a hexagonal bin. That is, for each \(y \in \mathbfit{Y}\), we
can (uniquely) identify the hexagon that the point belongs to. This
identification is done finding the nearest bin centroid for the \kD{}
points by considering the \kD{} Euclidean distance.

When \(k=2\), the starting coordinates \((s_1, s_2)\) mark the lower
left of the grid. This is the bottom left bin centroid. By starting from
there, points are generated to fill the grid accounting \(b_1\),
\(b_2\), \(a_1\), and \(a_2\).
